---
title: "Brazilian Population"
subtitle: "by Expedito Pinto de Paula Junior"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
# Load DataSet
bpop <- read.csv("BrazilPopulation.csv", header = TRUE, sep = ";", dec = ",")
```

Column {data-width=650}
-----------------------------------------------------------------------

### Mapping using "leaflet"

```{r}
library(leaflet)

df <- data.frame(name = bpop$StateName,
                 pop = bpop$Population,
                 lat = bpop$Lat,
                 lng = bpop$Lon)


df %>% 
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 2, radius = sqrt(bpop$Population) * 50, popup = 
      paste("<b>State: </b><a href='", bpop$StateLink,"'>",bpop$StateName," - ", bpop$State, "</a><br>",
            "<b>Population: </b>",bpop$Population, "<br>",
            "<b>Equivalent Country: </b><a href='",bpop$CountryLink,"'>",bpop$Equivalent_Country,"</a>"), group="int")

```

Column {data-width=350}
-----------------------------------------------------------------------
### Total and Ranking

#### Total Population: **`r sum(bpop$Population)`**

```{r}
knitr::kable(bpop[c("Rank","StateName","Population")])
```

### General Info

#### **DataSet**

- Dataset it was created based in Wikipedia [Brazilian Population by State](https://pt.wikipedia.org/wiki/Lista_de_unidades_federativas_do_Brasil_por_popula%C3%A7%C3%A3o).  

- This board was created using **flashdashboard** and **leaflet** library.

- Click in circles to see more details.

#### **Author**
- Designed by:  **Expedito Pinto de Paula Junior**
- Course: **Developing Data Products**
- Date: **Nov, 16 2020**




